Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-04-08 article.tex
on-going modifications

\title{Modelling the Co-evolution of Trade and Culture in the Roman Market}

@@

In order to validate our model we first reproduce common results from the literature on cultural transmission. We then show that it is possible to transform our model to fit processes that are economically sound, i.e. . To achieve these two goals, we have design for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).

@@

The neutral model is tested through ten experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining four experimental setups are using 3 goods, 500 agents and the same four values of $\mu$ (0.004,0.016 and 0.064). For each setup we have performed 100 runs of 10000 timestep each.

@@

>>>>

\title{Modelling the Co-evolution of Trade and Culture in Past Societies}

@@

In order to validate our model we first reproduce common results from the literature on cultural transmission. We then show that it is possible to transform our model to fit processes that are economically sound, i.e. the model should show the convergence optimal values such as shown in~\cite{gintis_emergence_2006}. To achieve these two goals, we have design for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).

@@

The neutral model is tested through seven experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining experimental setup is using 3 goods, 500 agents and $\mu$ equal to 0.004. For each setup we have performed 100 runs of 10000 timestep each.

@@

Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods. The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.
